### 2019-03-21 5_evaluation.tex
More text for section 5.

\subsection{Comparison with Published Results}

>>>>

Also of interest is the ability of asynchronous systems to be able to
hide communication latencies in the presence of task
parallelism. Figure~\ref{fig:efficiency-communication} plots task
granularity vs efficiency curves for varying amounts of
communication. The degree of communication is configured by the number
of bytes produced by each task (and therefore communicated with each
task dependency).

Asynchronous systems such as Charm++ are able to show two benefits in
these plots. First, by overlapping communication with computation,
such systems are able to execute smaller task granularities at higher
levels of efficiency compared to the bulk synchronous MPI
implementation. Second, the asynchrony also makes the curves smoother,
as spikes in latency due to interference from other jobs can be
mitigated, leading to more predictable performance, especially at
smaller message sizes.
